### 2019-06-03 Documents/literature_review/pages/review_content.tex
Changes; - Added more content to the new lit' review structure

\section{Literature Review}
\subsection{Fingerprint representation comparison}

@@

\subsection*{Effective schemes}
Results 
from the literature consistently show the effectiveness of language based encodings (Words or Sentences). This was shown in \cite{dechand2016empirical}, \cite{tan2017can} and \cite{kainda2009usability} with the accuracy of these schemes all being above 94.00\%. In all cases these were the best scemes in terms of accuracy. The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\% (Comparisons of methodology will be discussed in later sections).
\\\\
Aside from textual representations were graphical schemes. Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/} to name a few. Accuracy from these schemes were mixed with positive results obtained by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} where their best accuracy was achived by Random Art (94.00\%) and Flag Ext.\footnote{The authors' own improvement on Flag}(88.00\%). On the other hand, the worst accuracy was obtained by Flag(50\%). The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
In terms of usability of graphical schemes the literature concurred on their ease-of-use. In terms of speed of comparison all schemes consistently obtained some of the quickest comparisons times. This is also supported indirectly from the the comparison results of alternative literature \cite{kainda2009usability}\cite{dechand2016empirical} where with these in consideration graphical schemes still remain the quickest overall.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers including graphical schemes in their comparison. This is, therefore, a candidate for further research.

\subsection*{Experimentation comparison}

>>>>

\section{Literature Review}

@@

\subsection*{Definition of terms}
Throughout the paper various terms will be used to define elements of the authentication ceremony relevant to fingerprints verification. In this section well defined definitions will me made. This is to remove ambiguity and underlying associations readers may have for the words chosen.

\textbf{\textit{Encoding scheme}} - This is the physical method of encoding used to represent the fingerprint. For example ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.

\textbf{\textit{Method of comparison}} - This is the way in which the encoding scheme is assessed by the user. The most common example and the one used as default is ``Compare-and-Confirm''. This as the name suggests is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{compared}. Further examples of these method of comparisons will be explained in later sections.

\subsection{Fingerprint representation comparison}

\subsection*{Encoding scheme performance}
Results 
from the literature consistently show the effectiveness of language based encodings (Words or Sentences). This was shown in \cite{dechand2016empirical}, \cite{tan2017can} and \cite{kainda2009usability} with the accuracy of these schemes all being above 94.00\%. In all cases these were the best scemes in terms of accuracy. The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\% (Comparisons of methodology will be discussed in later sections).
\\\\
Aside from textual representations were graphical schemes. Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/} to name a few. Accuracy from these schemes were mixed with positive results obtained by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} where their best accuracy was achived by Random Art (94.00\%) and Flag Ext.\footnote{The authors' own improvement on Flag}(88.00\%). On the other hand, the worst accuracy was obtained by Flag(50\%). The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
In terms of usability of graphical schemes the literature concurred on their ease-of-use. In terms of speed of comparison all schemes consistently obtained some of the quickest comparisons times. This is also supported indirectly from the the comparison results of alternative literature \cite{kainda2009usability}\cite{dechand2016empirical} where with these in consideration graphical schemes still remain the quickest overall.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with only two papers including graphical schemes in their comparison. This is, therefore, a candidate for further research.

One unique paper in this research area was the work by \textbf{M. Shirvanian \textit{et al.}}\cite{shirvanian2017pitfalls} produced in the context of secure messaging pairing. This paper was unique for a number of reasons. First was to consideration for ``remote-vs-proximity'' pairing where, this is the first consideration of this aspect found in the literature. Second, was their studies aim into investigating fingerprint security and usability in a end-to-end encryption context. The study compared Numerical, Visual and Auditory representations. This is a standard setup for similar studies in the literature. QR code verification was also added to the proximity tests.

The findings from the paper showed a high false negative rate for all the schemes, this is a consideration also missing from the literature. Alongside this, results for usability were lower in a remote setting for all the schemes where the author comments on the expected nature of this result.\\
Images were assessed as being the most secure method of authentication in the remote setting, but voted as the method with the worst usability. This is highly inconsistent with all other work in this area. However, this could be due to the unique setting of remote verification resulting in distinct results from user studies. Without further work in this area it is difficult to conclusively validate these results.

To provide a visual comparison the accuracy results of the papers have been provided in Table~\ref{tab:results} \& \ref{tab:times}. Each paper used a unique metric for measuring effectiveness, and, therefore, have been translated into ``overall accuracy''.

\subsection*{Methods of comparison performance}
As explained in the definition section ``methods of comparison'' are the ways used to compare fingerprints. Aside from ``Compare-and-Confirm'' (CaC) there is: ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE). CaS is the method where one device displays the fingerprint and the other user is provided with a number of options, the user then has to choose the correct value from the list of candidates. If there is no match the user must deny the connection attempt. This was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}. CaE is designed for scenarios where both devices might not have a display, i.e. pairing between a phone and a keyboard. One device displays the checksum and the other device enters the string. The second device then compares the entered string and checks for a match.

Research has been performed assessing the performance of these schemes and how they affect the ultimate security of the authentication ceremony. The literature agrees on CaC being the best overall scheme to compare fingerprints \cite{tan2017can}\cite{uzun2007usability} with CaS being highlighted for its poor security and usability. CaE has  had contrasting results. \cite{uzun2007usability} discarded it after one round due to ``poor usability'', however, \cite{tan2017can} considered it the as the best method overall if usability and security is considered. This, therefore, shows how polarised the results are regarding CaE. This, however, could be due to the different overall use-cases of the studies. Validation of results from either study would, therefore, be an area of extra study.

One aspect of note from the work by \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} is their studies context  of  “Secure  device  pairing”  and  thus  some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example “Choose-and-Enter” (A participant chooses a passphrase from an available list and enters it into the other device).  Thus, only relevant comparison schemes and their results have been extracted and compared. \\

\subsection*{Experimentation methodology comparison}
To further look into the validity of previously discussed results it is necessary to asses how the respective studies reached these conclusions. Areas for consideration are scheme entropy, attacker strength and participant factors among others.\\
The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested. This makes it difficult to directly compare results and needs to be taken into consideration when comparing.
One of the papers this most affects is the early work by \textbf{Hsu-Chun Hsiao, \textit{et al.}} where their highest entropy is 28-bits. This was small even at the time of publication. There is an attempt by the authors' to address this issue in the later stages of the paper where they write \textit{``[...] increasing entropy is not a solution because it sacrifices usability and accuracy. With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}. Although the assumptions in this statement could be seen as following common sense they fail to consider the implications of of a small entropy on the security of the system.
\\
This leads into the assessment of attacker strength considerations made by each paper. Some papers failed to directly address their attacker strength consideration, but the overall strength has been infered from the changes made to their schemes. For example, if they decided to change a single character in a 40-digit (160-bit) SHA-1 hex digest they are indirectly stating that the attacker can control 39-digits (156-bit). To achieve this the attacker would have to compute $2^{156}$ SHA-1 compressions to find a key match.
In the literature this element ranged from $2^{28}$ to around $2^{242}$, however, this has some relation to the size of the encoding schemes used.
\\
In terms of the studies performed they all considered demographical data when presenting their results. Their average ages were all around $\sim35$ years old with the majority of participants being educated with at least a bachelor degree. This was alongside the equal split between male and female.

One consideration of note is that made by Dechand \textit{et al.} \cite{dechand2016empirical} where they briefly consider medical conditions such as ADHD and reading or visual disorders and they way they affect the comparison's effectiveness. They highlight on a slight reduction in accuracy but due to their small sample size they cannot conclusively validate these results. This is an aspect unique to all other literature, further work would be required to produce conclusive results, thus showing a gap in the literature.

One glaring issue with the demographical health of \textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} study is the use of two entirely different groups of participants. Not only were their demographics different but they were from different countries (America and Finland). This issue is of a concern due to the dual study design of this paper. Changes were made pragmatically regarding the results from the first round of 40 participants. These were then re-assessed and the results were directly compared. This puts huge doubts on the validity of the results with no consideration made by the authors to control external factors that may effect the methods performance.

\textbf{TODO: } Do an overall comparison of the sizes of the studies and link to the table produced

\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_attacker_stren.tex}
    }%
    \caption{Paper attribute comparison}
    \label{tab:attacker}
\end{table}
